The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-30 paper.tex
update

The gamma-ray emissivity\
is computed for each computational volume element in our simulations\
using the Klein–Nishina IC cross-section \citep{Jones1968} based\
on the simulated CR number density and the ISRF model given by \citep{Porter2017}.

>>>>

The gamma-ray emissivity\
is computed for each computational volume element in our simulations\
using the Klein–Nishina IC cross-section \citep{Jones1968} based\
on the simulated CR number density and the ISRF model given by \citet{Porter2017}.
